SMT-Boosted Security Types for Low-Level MPC

### 2025-05-09 esop25/new-cpj.tex
checkpoint

\renewcommand{\unity}[2]{U(#1, #2)}
\renewcommand{\ty}{T}
\newcommand{\eset}{D}
\newcommand{\dty}[2]{\langle #1, #2 \rangle}
\newcommand{\sharet}[1]{\mathrm{shares}(#1)}
\newcommand{\cvec}[1]{[#1]}
\newcommand{\secopent}{\mathrm{secopen}}
\newcommand{\declasst}[1]{\mathrm{declass}(#1)}
\renewcommand{\view}{\mathit{view}}
\newcommand{\revealed}{\mathit{revealed}}

@@

\begin{definition}[Adversarial Views]
  Given $\prog, \eqs, \Gamma$ with $\toeq{\prog} \models \eqs$ and $\varnothing, \eqs \vdash \prog : \Gamma$.
  Then for all $H,C$, define:
  $$
  \view(\Gamma,\eqs,C,\prog) \defeq \bigcup_{X \in (\pow(\vars(\prog)_C)) - \varnothing} \ty
     \qquad \text{where}\ \Gamma,\eqs \vdash \Sigma_{x \in X} x : \ty
  $$
\end{definition}

@@

\begin{theorem}[Security Typing]
  Given $\prog, \eqs, \Gamma$ with $\toeq{\prog} \models \eqs$ and $\varnothing, \eqs \vdash \prog : \Gamma$.
  The $\prog$ satisfies {NIMO} for ideal functionality $\idealf$ if for all $H,C$, we have:
  $$
  \revealed(\view(\Gamma,\eqs,C,\prog),H) = \setit{\idealf}
  $$
\end{theorem}

\subsection{Strategies}

\begin{mathpar}
  \inferrule[Sharing]
      {
        \eqs \models \mx{w_1}{\cid_1} \fplus \cdots \fplus \mx{w_n}{\cid_n} \eop \phi \\
        \\
        \exists R\ .\ (\forall M \in \pow(\setit{\mx{w_1}{\cid_1},\ldots,\mx{w_n}{\cid_n}})\ .\ 0 < |M| < n \implies \\
          \qquad \Gamma, \eqs \vdash \Sigma_{x \in M} x : \unity{R'}{\eset} \ \wedge \ R' \subseteq R)
      }   
      {\Gamma,R,\eqs \vdash \cvec{\mx{w_1}{\cid_1},\ldots,\mx{w_n}{\cid_n}} : \sharet{\phi}}

  \inferrule[Homomorphic Addition]
      {
       \Gamma,R_1,\eqs \vdash \cvec{\mx{w^1_1}{\cid_1},\ldots,\mx{w^1_n}{\cid_n}} : \sharet{\phi_1} \\
       \Gamma,R_2,\eqs \vdash \cvec{\mx{w^2_1}{\cid_1},\ldots,\mx{w^2_n}{\cid_n}} : \sharet{\phi_2} \\
       \eqs \models \mx{w_1}{\cid_1} \eop \mx{w^1_1}{\cid_1} \fplus \mx{w^2_1}{\cid_1} 
       \ \ldots\ 
       \eqs \models \mx{w_n}{\cid_n} \eop \mx{w^1_n}{\cid_n} \fplus \mx{w^2_n}{\cid_n} 
      }
      {
        \Gamma, R_1;R_2, \eqs \vdash \cvec{\mx{w_1}{\cid_1},\ldots,\mx{w_n}{\cid_n}} : \sharet{\phi_1 \fplus \phi_2}
      }

 \inferrule[Secure Opening]
      {
        \Gamma,R_1,\eqs \vdash \cvec{\mx{w_1}{\cid_1},\ldots,\mx{w_n}{\cid_n}} : \sharet{\phi} \\
        \eqs \models \px{w_1} \eop \mx{w_1}{\cid_1}
        \ \ldots\
        \eqs \models \px{w_n} \eop \mx{w_n}{\cid_n}\\
        \Gamma,\eqs \vdash \phi : \unity{R_2}{\eset}
      }
      {
        \Gamma, R_1;R_2, \eqs \vdash \cvec{\px{w_1},\ldots,\px{w_n}} : \secopent
      }

 \inferrule[Declassification]
      {
        \Gamma,R,\eqs \vdash \cvec{\mx{w_1}{\cid_1},\ldots,\mx{w_n}{\cid_n}} : \sharet{\phi} \\
        \eqs \models \px{w_1} \eop \mx{w_1}{\cid_1}
        \ \ldots\
        \eqs \models \px{w_n} \eop \mx{w_n}{\cid_n}
      }
      {
        \Gamma, R, \eqs \vdash \cvec{\px{w_1},\ldots,\px{w_n}} : \declasst{\phi}
      }
\end{mathpar}

>>>>

\renewcommand{\unity}[2]{U(#1, #2)}
\renewcommand{\ty}{T}
\newcommand{\eset}{D}
\newcommand{\dty}[2]{\langle #1, #2 \rangle}
\newcommand{\sharet}[1]{\mathrm{shares}(#1)}
\newcommand{\cvec}[1]{[#1]}
\newcommand{\secopent}{\mathrm{secopen}}
\newcommand{\declasst}[1]{\mathrm{declass}(#1)}
\renewcommand{\view}{\mathit{view}}
\newcommand{\revealed}{\mathit{revealed}}
\newcommand{\sty}{\varsigma}
\newcommand{\noise}{\mathrm{noise}}
\newcommand{\owners}{\mathrm{owners}}
\newcommand{\federation}{I_{\mathit{fed}}}

@@

\begin{definition}[Views]
  Given $\prog, \eqs, \Gamma$ with $\toeq{\prog} \models \eqs$ and $\varnothing, \eqs \vdash \prog : \Gamma$.
  Define:
  $$
  \view(\Gamma,\eqs,X) \defeq \bigcup_{X' \in (\pow(X) - \varnothing)} \ty
     \qquad \text{where}\ \Gamma,\eqs \vdash \Sigma_{x \in X'} x : \ty
  $$
\end{definition}

@@

\begin{theorem}[Security Typing]
  Given $\prog, \eqs, \Gamma$ with $\toeq{\prog} \models \eqs$ and $\varnothing, \eqs \vdash \prog : \Gamma$.
  Then $\prog$ satisfies {NIMO} for ideal functionality $\idealf$ if for all $H,C$, we have:
  $$
  \revealed(\view(\Gamma,\eqs,\vars(\prog)_C),H) = \setit{\idealf}
  $$
\end{theorem}

\subsection{Strategy Typings}

$$
\inferrule
    {\Gamma, \eqs \vdash \phi : \dty{R}{\eset} \\ R - R_I \neq \varnothing}
    {\Gamma, \eqs \vdash \phi : \noise(R,I)}
$$

\begin{mathpar}
  \inferrule[Sharing]
      {
        \eqs \models \mx{w_1}{\cid_1} \fplus \cdots \fplus \mx{w_n}{\cid_n} \eop \phi \\
        \\
        \exists R_2\ .\ (\forall M \in \pow(\setit{\mx{w_1}{\cid_1},\ldots,\mx{w_n}{\cid_n}})\ .\ 0 < |M| < n \implies \\
          \qquad \Gamma, \eqs \vdash \Sigma_{x \in M} x : \noise(R,\owners(M)) \ \wedge \ R \subseteq R_2)
      }   
      {\Gamma,\eqs \vdash R_1,\Delta \leadsto R_1;R_2, \Delta; \cvec{\mx{w_1}{\cid_1},\ldots,\mx{w_n}{\cid_n}} : \sharet{\phi}}

  \inferrule[Homomorphic Addition]
      {
       \Delta(\cvec{\mx{w^1_1}{\cid_1},\ldots,\mx{w^1_n}{\cid_n}}) = \sharet{\phi_1} \\
       \Delta(\cvec{\mx{w^2_1}{\cid_1},\ldots,\mx{w^2_n}{\cid_n}}) = \sharet{\phi_2} \\
       \eqs \models \mx{w_1}{\cid_1} \eop \mx{w^1_1}{\cid_1} \fplus \mx{w^2_1}{\cid_1} 
       \ \ldots\ 
       \eqs \models \mx{w_n}{\cid_n} \eop \mx{w^1_n}{\cid_n} \fplus \mx{w^2_n}{\cid_n} 
      }
      {
        \Gamma, \eqs \vdash R,\Delta \leadsto R,\Delta;\cvec{\mx{w_1}{\cid_1},\ldots,\mx{w_n}{\cid_n}} : \sharet{\phi_1 \fplus \phi_2}
      }

 \inferrule[Secure Opening]
      {
        \Delta(\cvec{\mx{w_1}{\cid_1},\ldots,\mx{w_n}{\cid_n}}) = \sharet{\phi} \\
        \eqs \models \px{w_1} \eop \mx{w_1}{\cid_1}
        \ \ldots\
        \eqs \models \px{w_n} \eop \mx{w_n}{\cid_n}\\
        \Gamma,\eqs \vdash \phi : \noise(R_2, \federation)
      }
      {
        \Gamma, \eqs \vdash R_1;\Delta \leadsto R_1;R_2, \Delta; \cvec{\px{w_1},\ldots,\px{w_n}} : \secopent
      }

 \inferrule[Declassification]
      {
        \Delta(\cvec{\mx{w_1}{\cid_1},\ldots,\mx{w_n}{\cid_n}}) =  \sharet{\phi} \\
        \eqs \models \px{w_1} \eop \mx{w_1}{\cid_1}
        \ \ldots\
        \eqs \models \px{w_n} \eop \mx{w_n}{\cid_n}
      }
      {
        \Gamma, \eqs \vdash R, \Delta \leadsto R, \Delta;\cvec{\px{w_1},\ldots,\px{w_n}} : \declasst{\phi}
      }
\end{mathpar}

\begin{theorem}
  Given $\prog, \eqs, \Gamma$ with $\toeq{\prog} \models \eqs$ and $\varnothing, \eqs \vdash \prog : \Gamma$.
  Suppose also $\Gamma,\eqs \vdash \varnothing,\varnothing \Rightarrow \Delta$, and define:
  $$\eset = \{ \phi \mid \exists \nu \in \dom(\Delta) . \Delta(\nu) \mapsto \declasst{\phi} \}$$.
  Then for any $H,C$, with:
  $$
  X_C \defeq \{ x \mid x \in \vars(\prog)_C \wedge \neg \exists \nu \in \dom(\Delta) . x \in \nu \}
  $$
  we have:
  $$
  \eset \cup  \revealed(\view(\Gamma,\eqs,X_C),H) = \revealed(\view(\Gamma,\eqs,\vars(\prog)_C),H)
  $$
\end{theorem}
